Next Trippy Structures\thanks{Supported by organization x.}

### 2019-01-28 paper.tex
Trajectory mining

@@

\subsection{Trajectory data mining}
Cite ways of obtaining the data we need, to show that it's possible even though we couldn't get any. You can get a lot of info from smart cards \cite{bhaskar2015passenger}, smart cards + gps \cite{ma2014development}, and even cellphone data \cite{liu2017exploring}. These guys also focus on trajectory reconstruction \cite{tao2014exploring}. These guys \cite{wang2014aggregated} made it so boring that they are probably not worth citing, but I'm keeping them here for now because they separate fridays and types of days, even though we don't care much about that anymore. OR DO WE? To the ones who wonder how do we know the final stops, they figured it out in \cite{alsger2016validating}. Basically what we need is called \textbf{trip-chaining}.

\subsection{Background structures and algorithms}
CSA. Brief explanation about WMs here. Explain ZSTD and applications.

>>>>

These guys \cite{wang2014aggregated} made it so boring that they are probably not worth citing, but I'm keeping them here for now because they separate fridays and types of days, even though we don't care much about that anymore. OR DO WE?

@@

\subsection{Trajectory data mining}
Currently there are several known techniques that would allow to collect data regarding users' trips over a public transportation network. Numerous works exist where these trajectories are mined from the transactions of smart cards (\cite{bhaskar2015passenger}, \cite{wang2014aggregated}). This can be complemented with information derived from GPS devices, as shown in \cite{ma2014development}. Alternatively, these trajectories may be extracted relying on positioning obtained from cellular networks, as proven by \cite{liu2017exploring}.

In addition, the authors of \cite{tao2014exploring} have specifically tackled the challenge of reconstructing full trajectories, accounting for trip-chaining, using data obtained from smart cards. Furthermore, in \cite{alsger2016validating} it is also proven that not only the alighting stops, but also the (last) destination stop of a trip can be estimated from boarding data gathered by a smart card, within a reasonable accuracy.

This summarized review proves that, although we were not able to access real data from a public transportation company, such curated information about users' trips can indeed be obtained and used for our proposed representation.

\subsection{Background structures and algorithms}
CSA. Brief explanation about WMs here. Explain ZSTD and applications?
